Deterministic Scheduling of Periodic Messages in a Network

### 2017-07-13 article/article.tex
typos, figure

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{url}
\usepackage{graphicx,graphics} 
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{complexity}
\usepackage{tkz-graph}
\usepackage{float}
\usepackage{setspace}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{authblk}
% \usepackage{hyperref}

@@

\todo{citation [7] pour les reseaux points a points ?}
 In this article, we study mechanisms to deal with the latency and periodicity constraints in the fronthaul network. \todo{The fronthaul network is the network located between the BUUs and the RRHs.
 Statistical multiplexing even with a large bandwidth does not comply with the latency requirements. Therefore, the current solution~\cite{pizzinat2015things,tayq2017real} is to use dedicated circuits. Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches. This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations. Here we propose to use a deterministic approach to schedule our periodic messages. This approach has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, as well at IETF DetNet working group~\cite{ieee802}. Several patents on concepts and mechanisms for DetNet have been already published, see for example~\cite{howe2005time,leclerc2016transmission}. The aim is to operate a C-RAN on a low-cost shared switched network.

@@

 In this section we always assume that the size of a message $\tau$ is equal to one. 
 We will prove the hardness of PRA and PALL for $\tau =1$ which implies the hardness of the general problems. 
Consider an instance of the problem PRA, i.e., a routed network $(G,\cal{R})$ and a period $P$.
The {\bf conflict depth} of an edge is the number of routes to which the edge belongs. 
The conflict depth of a routed network $(G,\cal{R})$ is the maximum of the conflict depth of its edges.
The {\bf load} of a routed network is the maximal number of routes sharing the same arc.
Remark that a $(P,1)$-periodic assignment must satisfy that $P$ is larger or equal to the load.

@@

	Often in real networks, the length of the routes are not arbitrary and we may exploit that to solve PALL easily. For instance if all the weights on the arcs $(c_t,t_i)$ are the same, we can replace them all by $0$ and substract this weight to $T_{max}$.
	The assignment in that case is trivial, just send all messages so that they follow each other without gaps in the central arc $(c_s,c_t)$. Since the arcs $(c_t,t_i)$ are of weigth $0$, all messages will go through $(c_t,c_s)$ on their way back in
	the same order and thus will not collide.

	A more realistic assumption would be that all weigths of the arcs $(s_i,c_s)$ are the same. It would correspond to a situation where all the BBUs are in the same datacenter.

@@

        The offset of the route $r_i$ is set to $i\tau$, which ensures that there are no collision on the way forward (on the arc $(c_s,c_t)$) as soon as $P \geq n\tau$ which is the minimal possible period. We set the waiting time for the route $i$ to $w_i = 2(\lambda(r_{0}) - \lambda(r_{i}))$. We can compute the time at which the message of the route $r_i$ arrives at the vertex $c_t$ on its way back: $t((c_t,c_s),r_i) = w_i + i\tau + 2\lambda(r_{i})$
        by replacing $w_i$ by its value we obtain $t((c_t,c_s),r_i) =  i\tau + 2\lambda(r_{0})$
        As a conclusion there are no collision on the edge $(c_t,c_s)$ as soon as the 
        period is larger than $n\tau$ (there are no gaps between the messages).

@@

     We now present a variant of the previous algorithm that we call {\bf Periodic Minimal Latency Scheduling (PMLS)}
     which takes into account the periodicity. We fix arbitrarily a backward route so that its message is the first to go through the central arc at time $t$. Then we modify the deadline of each forward route to be the minimum of their previous deadline and $t + P$.  We execute this algorithm for every possible first backward route while no solution is found. Since we run the previous algorithm at most $n$ times, the complexity is in $O(n^3\log(n))$. Remark that it will always find more solution than MLS,
     because if MLS find a solution with first route $r$ and such that $m_n - m_1 \leq P -\tau$, then this solution will be found by PMLS when it selects $r$ as the first route. Moreover when PMLS finds a solution, it is always a $(P,\tau)$ periodic assignment
     since we guarantee that all messages are scheduled in a period of time of size $P$ and it satisfies $MT({\cal M}) < T_{max}$ by construction of the deadlines. The scheduling algorithm we use always finds a solution to the  original problem it solves. However, in our periodic context, we do not allow to choose an offset for a route after $t+P- \tau$ which modulo $P$ may not collide with another route. Therefore PMLS may fail while there is a solution.

@@

       \begin{center}
     % \includegraphics[scale=0.4]{stochastic.pdf}
       \input{figures/stochastic}
      \end{center}
      \caption{Needed margin with respect to the period for a stochastic policy}
      \label{fig:sto}
     \end{figure}

>>>>

\documentclass[a4paper,10pt]{article}
%\documentclass[10pt, conference, letterpaper]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{url}
\usepackage{graphicx,graphics} 
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{complexity}
\usepackage{tkz-graph}
\usepackage{float}
\usepackage{setspace}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{authblk}
% \usepackage{hyperref}

@@

\todo{citation [7] pour les reseaux points a points ?}
 In this article, we study mechanisms to deal with the latency and periodicity constraints in the fronthaul network. \todo{The fronthaul network is the network located between the BUUs and the RRHs.}
 Statistical multiplexing even with a large bandwidth does not comply with the latency requirements. Therefore, the current solution~\cite{pizzinat2015things,tayq2017real} is to use dedicated circuits. Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches. This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations. Here we propose to use a deterministic approach to schedule our periodic messages. This approach has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, as well at IETF DetNet working group~\cite{ieee802}. Several patents on concepts and mechanisms for DetNet have been already published, see for example~\cite{howe2005time,leclerc2016transmission}. The aim is to operate a C-RAN on a low-cost shared switched network.

@@

 In this section we always assume that the size of a message $\tau$ is equal to one. 
 We will prove the hardness of PRA and PALL for $\tau =1$ which implies the hardness of the general problems. 
Consider an instance of the problem PRA, i.e., a routed network $(G,\cal{R})$ and a period $P$.
The {\bf conflict depth} of an arc is the number of routes to which the edge belongs. 
The conflict depth of a routed network $(G,\cal{R})$ is the maximum of the conflict depth of its arcs.
The {\bf load} of a routed network is the maximal number of routes sharing the same arc.
Remark that a $(P,1)$-periodic assignment must satisfy that $P$ is larger or equal to the load.

@@

	Often in real networks, the length of the routes are not arbitrary and we may exploit that to solve PALL easily. For instance if all the weights on the arcs $(c_t,t_i)$ are the same, we can replace them all by $0$ and substract this weight to $T_{max}$.It would correspond to a situation where all the BBUs are in the same datacenter.
	The assignment in that case is trivial, just send all messages so that they follow each other without gaps in the central arc $(c_s,c_t)$. Since the arcs $(c_t,t_i)$ are of weigth $0$, all messages will go through $(c_t,c_s)$ on their way back in
	the same order and thus will not collide.

 %A more realistic assumption would be that all weigths of the arcs $(s_i,c_s)$ are the same. It would correspond to a situation where all the BBUs are in the same datacenter.
	Another assumption would be that all weigths of the arcs $(s_i,c_s)$ are the same.

@@

        The offset of the route $r_i$ is set to $i\tau$, which ensures that there are no collision on the way forward (on the arc $(c_s,c_t)$) as soon as $P \geq n\tau$ which is the minimal possible period. We set the waiting time for the route $i$ to $w_i = 2(\lambda(r_{0}) - \lambda(r_{i}))$. We can compute the time at which the message of the route $r_i$ arrives at the vertex $c_t$ on its way back: $t(c_t,\rho_{r_i}) = w_i + i\tau + 2\lambda(r_{i})$
        by replacing $w_i$ by its value we obtain $t(c_t,\rho_{r_i}) =  i\tau + 2\lambda(r_{0})$
        As a conclusion there are no collision on the edge $(c_t,c_s)$ as soon as the 
        period is larger than $n\tau$ (there are no gaps between the messages).

@@

     We now present a variant of the previous algorithm that we call {\bf Periodic Minimal Latency Scheduling (PMLS)}
     which takes into account the periodicity. We fix arbitrarily a backward route so that its message is the first to go through the central arc at time $t$. Then we modify the deadline of each forward route to be the minimum of their previous deadline and $t + P$.  We execute this algorithm for every possible first backward route and we return the solution that minimize $MT({\cal M})$. Since we run the previous algorithm at most $n$ times, the complexity is in $O(n^3\log(n))$. Remark that it will always find more solution than MLS,
     because if MLS find a solution with first route $r$ and such that $m_{n-1} - m_0 \leq P -\tau$, then this solution will be found by PMLS when it selects $r$ as the first route. Moreover when PMLS finds a solution, it is always a $(P,\tau)$ periodic assignment
     since we guarantee that all messages are scheduled in a period of time of size $P$ and it satisfies $MT({\cal M}) < T_{max}$ by construction of the deadlines. The scheduling algorithm we use always finds a solution to the  original problem it solves. However, in our periodic context, we do not allow to choose an offset for a route after $t+P- \tau$ which modulo $P$ may not collide with another route. Therefore PMLS may fail while there is a solution.

@@

       \begin{center}
      \includegraphics[scale=0.4]{stochastic.pdf}
       %\input{figures/stochastic}
      \end{center}
      \caption{Needed margin with respect to the period for a stochastic policy}
      \label{fig:sto}
     \end{figure}
